---
title: "p8105_hw6_lk2761"
author: "Lorraine Kwok"
date: "November 19, 2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(modelr)
library(mgcv)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Problem 1

This problem utilizes data on children's birthweight and variables that may be related to this variable. 

This code chunk loads and tidies the data. 

```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform),
    babysex = recode(babysex, `1` = "male", `2` = "female"),
    frace = recode(frace, `1` = "white", `2` = "black", `3` = "asian", `4` = "puerto rican", `8` = "other", `9` = "unknown"),
    mrace = recode(mrace, `1` = "white", `2` = "black", `3` = "asian", `4` = "puerto rican", `8` = "other"),
    malform = recode(malform, `0` = "absent", `1` = "present")) %>%
  view()
```

This code chunk fits a regression model based on a hypothesized structure for factors that underly birthweight. The predictors included are mom's age (`momage`), average number of cigarettes smoked per day during the pregnancy (`smoken`), mother's pre-pregnancy BMI (`ppbmi`), mother's pre-pregnancy weight in pounds (`ppwt`) and mother's delivery weight in pounds (`delwt`). 

```{r}
fit = lm(bwt ~ momage + smoken + ppbmi + ppwt + delwt, data = birthweight)
```

This code creates a scatterplot comparing the residuals against the fitted values for my fitted model. 

```{r}
birthweight %>%
  modelr::add_residuals(fit) %>%
  modelr::add_predictions(fit) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

The following code chunk generates two other models: the first one using the length at birth and gestational age in weeks as predictors and the second one using head circumference, length, sex, and all interactions (including the three-way interaction) between these as predictors.

```{r}
fit_main = lm(bwt ~ blength + gaweeks, data = birthweight)

fit_interaction = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)
```

We will use `crossv_mc` and functions in `purrr` to compare the three models to each other. 

This code chunk creates the training and test datasets for the cross-validation. 

```{r}
cv_df = 
  crossv_mc(birthweight, 100) 

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

cv_df %>% pull(test) %>% .[[1]] %>% as_tibble
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

This code chunk fits models and obtains the root mean squared error (RMSE) values for each of the three models. 

```{r}
cv_df = 
  cv_df %>% 
  mutate(my_mod  = map(train, ~lm(bwt ~ momage + smoken + ppbmi + ppwt + delwt, data = .x)),
         main_mod  = map(train, ~mgcv::gam(bwt ~ blength + gaweeks, data = .x)),
         interaction_mod  = map(train, ~gam(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_my = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
         rmse_main = map2_dbl(main_mod, test, ~rmse(model = .x, data = .y)),
         rmse_interaction = map2_dbl(interaction_mod, test, ~rmse(model = .x, data = .y))) %>% 
  view()
```

This code generates a violin plot that compares the three models using the RMSE values for each candidate model. 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) + 
  geom_violin()
```

Based on the plot that is generated, I would select the model with head circumference, length, sex, and all interactions between these as predictors because it has the lowest RMSE of the three models. 

## Problem 2

This loads and tidies the weather data for Central Park, NY.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The next two code chunks draw 5000 bootstrap samples and saves them in two different dataframes: one with the r-squared value and one with the beta coefficients. 95% confidence intervals were also computed for the r-squared value and the log of the beta coefficients. 

```{r}
weather_r =
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>%
  janitor::clean_names() %>%
  mutate(
    lower_bound = quantile(r_squared, 0.025),
    upper_bound = quantile(r_squared, 0.975)
  )

weather_r
```

```{r}
weather_log =
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  janitor::clean_names() %>%
  select(id, intercept, tmin) %>%
  group_by(id) %>%
  summarise_all(na.omit) %>%
  mutate(
    log_betas = log(intercept*tmin),
    lower_bound = quantile(log_betas, 0.025),
    upper_bound = quantile(log_betas, 0.975)
  )

weather_log
```

The 95% confidence interval for r-squared is (0.894, 0.928). The 95% confidence interval for log(beta0 * beta1) is (1.966, 2.058). 

These two code chunks plot the distribution of the r-squared and 
log(beta0 * beta1) estimates, using density plots.

```{r}
weather_r %>%
  ggplot(aes(x = r_squared)) +
  geom_density() + 
  labs(title = "Distribution of R-squared estimates")
```

```{r}
weather_log %>%
  ggplot(aes(x = log_betas)) + 
  geom_density() +
  labs(title = "Distribution of log(beta0 * beta1) estimates")
```

The distribution of r-square estimates has a slight tail extending to low values, but it is not that heavy, which suggests the suggests the distribution is fairly symmetric (normally distributed) for the bootstrap sample. Similarly, the distribution of the log(beta0 * beta1) estimates looks symmetric (normally distributed). 