---
title: "p8105_hw6_lk2761"
author: "Lorraine Kwok"
date: "November 19, 2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Problem 1

This problem utilizes data on children's birthweight and variables that may be related to this variable. 

This code chunk loads and tidies the data. 

```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform),
    babysex = recode(babysex, `1` = "male", `2` = "female"),
    frace = recode(frace, `1` = "white", `2` = "black", `3` = "asian", `4` = "puerto rican", `8` = "other", `9` = "unknown"),
    mrace = recode(mrace, `1` = "white", `2` = "black", `3` = "asian", `4` = "puerto rican", `8` = "other"),
    malform = recode(malform, `0` = "absent", `1` = "present")) %>%
  view()
```

This code chunk fits a regression model. The predictors included are `momage`, `smoken`, `ppbmi`, `ppwt` and `delwt`.  

```{r}
fit = lm(bwt ~ momage + smoken + ppbmi + ppwt + delwt, data = birthweight)
```

This code creates a scatterplot comparing the residuals against the fitted values. 

```{r}
birthweight %>%
  modelr::add_residuals(fit) %>%
  modelr::add_predictions(fit) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

The following code chunk generates two other models.

```{r}
fit_main = lm(bwt ~ blength + gaweeks, data = birthweight)

fit_interaction = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)
```

We will use `crossv_mc` to compare the three models to each other. 

```{r}
cv_df = 
  crossv_mc(birthweight, 100) 

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

cv_df %>% pull(test) %>% .[[1]] %>% as_tibble
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(my_mod  = map(train, ~lm(bwt ~ momage + smoken + ppbmi + ppwt + delwt, data = .x)),
         main_mod  = map(train, ~mgcv::gam(bwt ~ blength + gaweeks, data = .x)),
         interaction_mod  = map(train, ~gam(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_my = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
         rmse_main = map2_dbl(main_mod, test, ~rmse(model = .x, data = .y)),
         rmse_interaction = map2_dbl(interaction_mod, test, ~rmse(model = .x, data = .y))) %>% view()
```

```{r}
cv_df %>% 
  dplyr::select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

